---
title: "step4a regression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




# possible mistake?  why model n_comorbidity n_pos_comorb as continous variable?
```{r}
final_dat_complete <- final_dat %>% 
  dplyr::select(t_30, death, cancer, age_gp, gender, race_gp, n_comorbity_gp, n_posi_comorb_gp, surgery_4w) %>% 
  drop_na() 

library(survival)
survival_model_all <- coxph(Surv(t_30, death) ~ (cancer + age_gp + gender + race_gp
                            + n_comorbity_gp + n_posi_comorb_gp + surgery_4w) ^2, data = final_dat_complete)

summary(survival_model_all)
```
```{r}
library(MASS)
stepAIC(survival_model_all, direction='backward', trace = FALSE)
```


```{r}
dat <- final_dat %>% filter(age_gp != '>= 75')
coxph(formula = Surv(t_30, death) ~ cancer + age_gp + gender + 
    race_gp + n_comorbity_gp + n_posi_comorb_gp + surgery_4w +  age_gp:gender + 
    age_gp:race_gp + age_gp:n_comorbity_gp + age_gp:n_posi_comorb_gp + 
    age_gp:surgery_4w + gender:race_gp + gender:n_comorbity_gp + 
    race_gp:n_posi_comorb_gp + race_gp:surgery_4w + n_comorbity_gp:n_posi_comorb_gp + 
    n_comorbity_gp:surgery_4w, data = dat)
```


```{r}
library(survminer)
model_surv_3 <- survfit(Surv(t_30, death) ~ cancer + age_gp, data = final_dat_complete) 
ggsurvplot(model_surv_3, data = final_dat_complete, risk.table = 'absolute', pval = TRUE, surv.median.line = 'hv', ylim=c(0.7, 1))
```



```{r}
options(digits=3)
res <- summary(survival_model_all)
# str(res)
res$coefficients
```


```{r}

# dat <- final_dat %>% 
#   select(cancer_type, chemo_4w, radiation_4w, survive_5yr_more, age_gp, gender, 
#          race_gp, n_comorbity, n_posi_comorb, surgery_4w)
# Hmisc::rcorr(dat)
```

# need to check interaction?
```{r}
survival_model_cancer <- coxph(Surv(t_30, death) ~ cancer_type + chemo_4w + 
                                 radiation_4w + survive_5yr_more + age_gp + 
                                 gender + race_gp + n_comorbity_gp + n_posi_comorb_gp +
                                 surgery_4w, data = dat_cancer)

summary(survival_model_cancer)
```


```{r}
res <- summary(survival_model_cancer)
# str(res)
res$coefficients
```




# ```{r}
# # data alltime;
# # set B.final_dat;
# # keep cancer T_30 death;
# # run;
# # PROC EXPORT DATA= WORK.alltime
# #             OUTFILE= "Z:\8 GQ Zhang group\STEP1 data analysis\alltime.csv"
# #             DBMS=CSV REPLACE;
# #      PUTNAMES=YES;
# # RUN;
# ```

```{r}
library(survival)
library("survminer")

#before matching;
fit <- survfit(Surv(t_30,  death) ~ cancer,data = final_dat)
ggsurvplot(fit, data = final_dat, ylim = c(0.85,1),conf.int = TRUE)
  
#after matching;
matched_data=read.csv(file="Z:\\8 GQ Zhang group\\STEP1 data analysis\\matched_data.csv",head=T)
fit_aftermatch <- survfit(Surv(T_30, death) ~ Cancer,data = matched_data)
ggsurvplot(fit_aftermatch, data = matched_data, ylim = c(0.85,1),conf.int = TRUE)

splots <- list()
splots[[1]] <- ggsurvplot(fit, data = final_dat,xlim=c(0,30), ylim = c(0.9,1),,xlab="Days since COVID diagnosis",conf.int = TRUE,censor=F,font.x = c(11,  "black"),font.y = c(11, "black"),linetype = 1,size = 1,palette = "lancet") 
splots[[2]] <- ggsurvplot(fit_aftermatch , data = matched_data, xlim=c(0,30),ylim = c(0.9,1),xlab="Days since COVID diagnosis",conf.int = TRUE,censor=F,font.x = c(11, "black"),
   font.y = c(11,  "black"),linetype = 1,size = 1,palette = "lancet")
   
arrange_ggsurvplots(splots, print = TRUE,
  ncol = 2, nrow = 1, risk.table.height = 0.4,ggtheme = theme_minimal())
```



```{r}
####################################PLOT FOR LUNG CANCER;
library(survival)
library("survminer")

#before matching;
final_dat=read.csv(file="Z:\\8 GQ Zhang group\\STEP1 data analysis\\alltime_lung_cancer.csv",head=T)
fit <- survfit(Surv(T_30,  death) ~ Cancer,data = final_dat)
  
#after matching;
matched_data=read.csv(file="Z:\\8 GQ Zhang group\\STEP1 data analysis\\matched_data_lung_cancer.csv",head=T)
fit_aftermatch <- survfit(Surv(T_30, death) ~ Cancer,data = matched_data)
ggsurvplot(fit_aftermatch, data = matched_data, ylim = c(0.85,1),conf.int = TRUE)

splots <- list()
splots[[1]] <- ggsurvplot(fit, data = final_dat,xlim=c(0,30), ylim = c(0.9,1),,xlab="Days since COVID diagnosis",conf.int = TRUE,censor=F,font.x = c(11,  "black"),font.y = c(11, "black"),linetype = 1,size = 1,palette = "lancet") 
splots[[2]] <- ggsurvplot(fit_aftermatch , data = matched_data, xlim=c(0,30),ylim = c(0.9,1),xlab="Days since COVID diagnosis",conf.int = TRUE,censor=F,font.x = c(11, "black"),
   font.y = c(11,  "black"),linetype = 1,size = 1,palette = "lancet")
   
arrange_ggsurvplots(splots, print = TRUE,
  ncol = 2, nrow = 1, risk.table.height = 0.4,ggtheme = theme_minimal())
  
```








```{r}
#  
# data matched_data;
# set matched;
# keep cancer T_30  death;
# run;
# PROC EXPORT DATA= WORK.matched_data  
#             OUTFILE= "Z:\8 GQ Zhang group\STEP1 data analysis\matched_data.csv" 
#             DBMS=CSV REPLACE;
#      PUTNAMES=YES;
# RUN;
```





```{r}
# proc logistic data=rawdata_cancer descending;
# class  age_gp(ref=first) gender(ref=first)    race_gp(ref="Non-hispanic white")
# Surgery_4w(ref=first)  cancer_type(ref=first)
# survive_5yr_more(ref=first)
# Radiation_4w(ref=first) chemo_4w(ref=first)
# / param=ref;
# model severity=age_gp gender  
# race_gp
# N_comorbity
# N_Posi_Comorb
# Surgery_4w
# cancer_type
# chemo_4w
# Radiation_4w 
# survive_5yr_more/selection=stepwise;
# ods output ParameterEstimates=Prob(where=(Variable~='Intercept') keep=
# variable ProbChiSq) OddsRatios=OR(keep=effect OddsRatioEst 
# LowerCL UpperCL);
# run;
```



# severity (binary)
```{r}
fit <- glm(severity ~ cancer_type + chemo_4w +radiation_4w + survive_5yr_more +
           age_gp + gender + race_gp + n_comorbity_gp + n_posi_comorb_gp +
             surgery_4w,
          family = binomial(), data = dat_cancer)

summary(fit)
# ols_step_both_p(fit, pent = 0.1, prem = 0.3, details = TRUE)
```
```{r}
# ***MODEL 3: Multinomial model;
# *severity, cancer;
# proc logistic data=rawdata_cancer descending;
# class  age_gp(ref=first) gender(ref=first)    race_gp(ref="Non-hispanic white")
# Surgery_4w(ref=first)  cancer_type(ref=first)
# survive_5yr_more(ref=first)
# chemo_4w(ref=first)
# Radiation_4w(ref=first) / param=ref;
# model  severity_level=age_gp gender  
# race_gp
# N_comorbity
# N_Posi_Comorb
# Surgery_4w
# cancer_type
# chemo_4w
# Radiation_4w 
# survive_5yr_more/link=glogit;
# ods output ParameterEstimates=Prob(where=(Variable~='Intercept')) OddsRatios=OR;
# run;



```


data Prob; set Prob; retain id 0; id=id+1; run;
data OR; set OR; retain id 0; id=id+1; run;
data MNP_cancer;merge Prob OR;by id;
MN_cancer=trim(left(put(OddsRatioEst,8.2)))||"("||
trim(left(put(LowerCL,8.2)))||","||trim(left(put(UpperCL,8.2)))||")";
drop OddsRatioEst LowerCL UpperCL;
run; 
proc datasets;delete Prob OR;quit;run;


*severity, non-cancer;
proc logistic data=rawdata_nocancer descending;
class  age_gp(ref=first) gender(ref=first)    race_gp(ref="Non-hispanic white")
Surgery_4w(ref=first) / param=ref;
model severity_level =age_gp gender  
race_gp
N_comorbity
N_Posi_Comorb
Surgery_4w/link=glogit;
ods output ParameterEstimates=Prob(where=(Variable~='Intercept')) OddsRatios=OR ;
run;
data Prob; set Prob; retain id 0; id=id+1; run;
data OR; set OR; retain id 0; id=id+1; run;
data MNP_nocancer;merge Prob OR;by id;
MN_nocancer=trim(left(put(OddsRatioEst,8.2)))||"("||
trim(left(put(LowerCL,8.2)))||","||trim(left(put(UpperCL,8.2)))||")";
drop OddsRatioEst LowerCL UpperCL;
run; 
proc datasets;delete Prob OR;quit;run;

proc sort data=MNP_cancer; by id; run;
proc sort data=MNP_nocancer; by id; run;

data MNP_cancer1; set MNP_cancer; where Response="1"; MN_cancer1=MN_cancer; nid=_n_; run;
data MNP_cancer2; set MNP_cancer; where Response="2"; MN_cancer2=MN_cancer; nid=_n_;run;
data MNP_cancer3; set MNP_cancer; where Response="3"; MN_cancer3=MN_cancer; nid=_n_;run;
 
data MNP_nocancer1; set MNP_nocancer; where Response="1"; MN_nocancer1=MN_nocancer; nid=_n_;run;
data MNP_nocancer2; set MNP_nocancer; where Response="2"; MN_nocancer2=MN_nocancer; nid=_n_;run;
data MNP_nocancer3; set MNP_nocancer; where Response="3"; MN_nocancer3=MN_nocancer; nid=_n_;run;
 
proc sort data=MNP_cancer1; by nid; run;
proc sort data=MNP_cancer2; by nid; run;
proc sort data=MNP_cancer3; by nid; run;
 
proc sort data=MNP_nocancer1; by nid; run;
proc sort data=MNP_nocancer2; by nid; run;
proc sort data=MNP_nocancer3; by nid; run;

data MNP;
merge MNP_cancer1 MNP_cancer2 MNP_cancer3  
MNP_nocancer1 MNP_nocancer2 MNP_nocancer3 ;
by nid;
run;
```{r}
library(nnet)
multinom_model_cancer <-  multinom(severity ~ cancer_type + chemo_4w +radiation_4w + survive_5yr_more +
           age_gp + gender + race_gp + n_comorbity + n_posi_comorb +
             surgery_4w,
          family = binomial(), data = dat_cancer)
summary(multinom_model_cancer)
```


# matching
```{r}
# *Export data to do matching;
# data DATA_FOR_MATCHING;
# set B.rawdata;
# keep Patient_ID cancer  GENDER   REGION age            
# race_gp N_comorbity N_Posi_Comorb  
# ;
# if Patient_ID="" 
# or  GENDER="Unknown" or     
# REGION="z: Other/Unkn"      
# or  age=. or cancer=.  or   
# N_comorbity=. or N_Posi_Comorb=. then delete; *delete missing except race because other and missing are mixed and there's a lot;
# run;

#match on cancer
# mydata <- read.csv ("data/Before_matching.csv")

dat_for_matching <- final_dat %>% 
  select(patient_id, cancer, gender, region, age_gp, race_gp, n_comorbity_gp, n_posi_comorb_gp, t_30, death) %>% 
  drop_na()
```