---
title: "step 4 main code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(qwraps2)
library(olsrr)
library(haven)
library(tidyverse)
library(magrittr)
library(summarytools)
library(gt)
```


```{r}
load('data/final_data.RData')
load('data/rawdata0.RData')
```

## a small helper function
```{r}
proc_freq <- function(data, vars) {
  for (var in vars) {
    print(var)
    print(freq(x = data[[var]]))
  }
}
```


## no surgery variable anymore
<!-- # final_dat -->
<!-- ```{r} -->
<!-- # ***Table 1 and 2; -->
<!-- # data final_dat; -->
<!-- # set B.final_dat; -->
<!-- # if gender="Unknown" then gender="z: Unknown"; *rename to make this category appear in the last row; -->
<!-- # if age_cancer_gp="miss" then age_cancer_gp="z: Unknown"; -->
<!-- # if age_gp="" then age_gp="z: Unknown"; -->
<!-- # if obese_overweight="" then obese_overweight="z: Unknown"; -->
<!-- # if Surgery_4w=1 then surgery4wk="Yes"; -->
<!-- # else if Surgery_4w=0 then surgery4wk="No"; -->
<!-- # else if Surgery_4w=. then surgery4wk="z: Unknown"; -->
<!-- # run; -->


<!-- final_dat <- main_data %>%  -->
<!--   # rowwise() %>%  # rowwise is wrong in this setting since levels will be check at each row??? -->
<!--   mutate( -->
<!--          # gender = ifelse(gender == 'Unknown', 'z: Unknown', gender), -->
<!--          # age_cancer_gp = ifelse(age_cancer_gp == 'miss', 'z: Unknown', age_cancer_gp), -->
<!--          # age_gp = factor(ifelse(is.na(age_gp), 'z: Unknown', age_gp), levels = c(levels(age_gp), 'z: Unknown')), -->
<!--          # obese_overweight = ifelse(is.na(obese_overweight), 'z: Unknown', obese_overweight), -->
<!--          # surgery4wk = ifelse(is.na(surgery_4w), 'z: Unknown',  -->
<!--          #                     ifelse(surgery_4w == 1 , "Yes", -->
<!--          #                     ifelse(surgery_4w == 0, 'No', NA))) -->
<!--         surgery4wk = surgery_4w -->
<!--          ) -->
<!-- #  -->
<!-- # final_dat$age_gp <- fct_explicit_na(final_dat$age_gp, na_level = 'z: Unknown') -->
<!-- ``` -->





```{r}
# proc datasets; delete S0-S20; run;
# %twoway_digital_Outcome(final_dat,cancer, 0,1,death,1 );
# %twoway_digital_Outcome(final_dat,cancer, 0,1,Inpatient,2 );
# %twoway_digital_Outcome(final_dat,cancer, 0,1,ICU,3);
# %twoway_digital_Outcome(final_dat,cancer, 0,1,Ventilation,4);
# %twoway_digital_Outcome(final_dat,cancer, 0,1,severity,5);
# %twoway_digital_Outcome(final_dat,cancer, 0,1,severity_level,6);
# 
# *independent variables;
# two_way_table(final_dat, cancer, 0,1, age_gp,7);
# two_way_table(final_dat,cancer, 0,1,gender,8);
# two_way_table(final_dat,cancer, 0,1,race_gp,9);
# two_way_table(final_dat,cancer, 0,1,Region,10);
# two_way_table(final_dat,cancer, 0,1,N_comorbity_gp,11);
# two_way_table(final_dat,cancer, 0,1,N_Posi_Comorb_gp,12);
# two_way_table(final_dat,cancer, 0,1,surgery4wk,13);
# two_way_table(final_dat,cancer, 0,1,cancer_type,14);
# %twoway_digital(final_dat,cancer, 0,1,chemo_4w,15);
# %twoway_digital(final_dat,cancer, 0,1,Radiation_4w,16);
# two_way_table(final_dat,cancer, 0,1,age_cancer_gp,17);
# %twoway_digital(final_dat,cancer, 0,1,survive_5yr_more,18);
  
```

<!-- ```{r} -->
<!-- table(final_dat$death, final_dat$cancer, useNA = 'no') -->
<!-- ``` -->


```{r}
# twoway_digital_outcome
```

```{r}
# table_data <- final_dat %>% 
#     select(row_var, col_var) %>% 
#     group_by(col_var)
```

```{r}
# # function to create two way table for two categorical variables
# two_way_digitial_outcome <- function(data, col_var, col_var_level, row_var, row_var_level) {
#   options(qwraps2_markup = "markdown")
#   
#   table_data <- final_dat %>% 
#     select(row_var, col_var) %>% 
#     group_by(col_var)
#     
#   our_summary1 <-
#     list(col_var =
#           list(
#               row_var_level[1] = ~ qwraps2::n_perc(row_var_level[1]== row_var_level[1], digits = 2),
#               row_var_level[2] = ~ qwraps2::n_perc(row_var_level[1] == row_var_level[2], digits = 2)
#               )
#          )
#   
#   group_part <- summary_table(table_data, our_summary1)
#   
#   
#   our_summary2 <-
#     list("death, n(%)" =
#           list(
#               row_var_level[1] = ~ qwraps2::n_perc0(row_var_level[1] == row_var_level[1], digits = 2),
#               row_var_level[2]  = ~ qwraps2::n_perc0(row_var_level[1] == row_var_level[2], digits = 2))
#     )
#   
#   row_sum_part <- summary_table(final_dat, our_summary2)
#   
#   
#   final_table <- cbind(row_sum_part, group_part)
#   
#   print(final_table,
#         cnames = c("total", "cancer0", "cancer1"))  
# }
```

```{r}
# options(qwraps2_markup = "markdown")
# 
# table_data <- final_dat %>% 
#   select(death, cancer) %>% 
#   group_by(cancer)
#   
# our_summary1 <-
#   list("death, n(%)" =
#         list(
#             "0" = ~ qwraps2::n_perc(death == 0, digits = 2),
#             "1"  = ~ qwraps2::n_perc(death == 1, digits = 2)
#             )
#        )
# 
# group_part <- summary_table(table_data, our_summary1)
# 
# 
# our_summary2 <-
#   list("death, n(%)" =
#         list(
#             "0" = ~ qwraps2::n_perc0(death == 0, digits = 2),
#             "1"  = ~ qwraps2::n_perc0(death == 1, digits = 2))
#   )
# 
# row_sum_part <- summary_table(final_dat, our_summary2)
# 
# 
# final_table <- cbind(row_sum_part, group_part)
# # 
# # final_table[, "level"] = c(0, 1)
# 
# # final_table[, c('level', 'final_dat', '0', '1')]
# 
# print(final_table,
#       cnames = c("total", "cancer0", "cancer1"))

```

<!-- ```{r} -->
<!-- tab <- table(final_dat$death, final_dat$cancer, useNA = 'no') -->
<!-- ``` -->


```{r}
# library(gmodels)
# a <- CrossTable(final_dat$death, final_dat$cancer, missing.include=FALSE,
#            format="SAS")
```



```{r}
library(crosstable)
library(rlang)
```



# two_way_table function
```{r}
#' create two-way cross-table
#'
#' @param data the data used 
#' @param row_var variable that appear in the row position
#' @param col_var variable that appear in the col position
#' @return formula object
#' @export
#' @examples
two_way_table <- function(data, row_var, col_var, keep_one_row_name = FALSE, margin="column", total="row", showNA = 'no', test=FALSE, ...) {
  col_levels <- levels(as.factor(data[[col_var]]))
  col_names <- paste(col_var, col_levels)
  cross_table <- crosstable(data = data, cols = all_of(row_var), by=col_var, margin=margin, total="row", showNA = showNA, test=test, ...) %>% 
    mutate(label=paste(row_var, ', n(%)')) %>% 
    rename(
      # UQ(paste(col_var,'0')) := '0',
      #      UQ(paste(col_var,'1')) := '1',
           'level' = 'variable',
           'variable' = 'label') %>% 
    select(-c('.id'))  
  
  # rename the column name of each level of column variable
  for (i in 1:length(col_levels)) {
    col_name <- col_names[i]
    col_level <- col_levels[i]
    cross_table <- rename(cross_table, !!sym(col_name) := !!sym(col_level))
  }
  
  # make the order of column the same as SAS
  cross_table <- cross_table %>% select(c('variable', 'level', 'Total', everything()))
  # only keep one column variable name
  if (keep_one_row_name == TRUE) {
    cross_table[2:nrow(cross_table), 'variable'] = ''
  }
  # only keep one test result for this row variable
  if(test==TRUE) {
    cross_table[2:nrow(cross_table), 'test'] = ''
  }
  
  return(cross_table)
}

```

```{r}
# crosstable(data = final_dat, cols = all_of(row_var), by=col_var, margin=margin, total="row", showNA = showNA, test=test, ...)
```


## define variable used to create descriptive table
```{r}
descriptive_table <- function(vars, by_var, data, ...) {
  data <- data %>% droplevels()
  
  tbl <- bind_rows(
  lapply(vars, two_way_table, data=data, col_var=by_var, keep_one_row_name = TRUE, ...)
  )
  
}
```

# outcome variables by cancer group


```{r}
var_list <- c('inpatient', 'ventilation', 'icu', 'death', 'severity', 'severity_level', 'death_on_month_0', 'death')

(table_outcome <- descriptive_table(var_list, 'cancer', final_dat, showNA = 'ifany'))

# table_outcome <- table_outcome %>% filter(level == '1')
# table_outcome <- rbind(table_outcome, two_way_table(final_dat, 'severity_level', 'cancer'))
# table_outcome
```




# independent variables

```{r}
var_list_demographic <- c('age_gp', 'gender', 'race_gp', 'region')

(table_demographic <- descriptive_table(var_list, 'cancer', final_dat, showNA = 'ifany'))

```





<!-- ```{r} -->
<!-- # cross_tbl <- CrossTable(final_dat$death, final_dat$cancer, missing.include=FALSE, -->
<!-- #            format="SAS") -->
<!-- #  -->
<!-- #  -->
<!-- # row1 <- c('', 'total', 'cancer0', 'cancer1') -->
<!-- # row2 <- c('death, n(%)', '', '', '') -->
<!-- # row3 <- c('0', tab['0', '0'] + tab['0', '1'], tab['0', '0'], tab['0', '1']) -->
<!-- # row4 <- c('1', tab['1', '0'] + tab['1', '1'], tab['1', '0'], tab['1', '1']) -->
<!-- # tabl <- as_tibble(rbind(row1, row2, row3, row4)) -->
<!-- ``` -->

```{r}
# library(knitr)
# library(kableExtra)
# tabl %>%
#   kable(col.names = NULL) %>%
#    kable_classic(full_width = F, html_font = "Cambria")
```


## create comorbidity table
```{r}
# crosstable(final_dat, var_lst, by='cancer') %>% 
#   select(everything()) %>% 
#   as_flextable()
```


```{r}
# var_lst = tolower(c('Chronic_Kidney_Disease', 
#                     'Chronic_Obstructive_Pulmonary',
#                     'Down_Syndrome',
#                     'Solid_Organ_Transplant',
#                     'obesity01',
#                     'pregnancy',
#                     'Heart_Failure',
#                     'Coronary_Artery_Disease',
#                     'Cardiomyopathies',
#                     'Sickle_Cell_Disease',
#                     'smoke_yn',
#                     'Type_2_Diabetes_Mellitus',
#                     'Asthma',
#                     'Cerebrovascular',
#                     'Cystic_Fibrosis',
#                     'Hypertension',
#                     'Other_Immuno',
#                     'Liver_Disease',
#                     'Dementia',
#                     'overweight01',
#                     'Pulmonary_Fibrosis',
#                     'Thalassemia',
#                     'Type_1_Diabetes_Mellitus'))

var_list <- c('charlson_comorbidity_index', 'n_comorbity_gp', 'any_malignancy', 'hiv', 
              'renal', 'hemiplegia', 'diabetes_with_cc',
              'diabetes_without_cc', 'severe_liver', 'mild_liver', 'peptic_ulcer', 
              'rheumatic', 'chronic_pulmonary', 'cerebrovascular', 'dementia',
              'peripheral_vascular', 'heart_failure', 'myocardial_infarction', 
              'obesity', 'cardiovascular', 'smoking_infarction', 'wheelchair',
              'dysphagia')

(table_comorbidity <- descriptive_table(var_list, 'cancer', final_dat, showNA = 'ifany'))


# com_indep <- com_indep %>% 
#   filter(level == 1)
# 
# com_indep
```

```{r}
var_list_covid_trt <- c('treatment_remdesivir',
                  'treatment_lopinavir_or_ritonavir',
                  'treatment_bamlanivimab', 
                  'treatment_casirivimab',
                  'treatment_tocilizumab',
                  'treatment_hydroxychloroquine')

(table_covid_trt <- descriptive_table(var_list_covid_trt, 'cancer', final_dat, showNA = 'ifany'))

```



## New table 1 descriptive table
```{r}
rbind(table_demographic, table_comorbidity, table_outcome, table_covid_trt)
```

# dat_cancer dat_nocancer 
# Table 3;
data rawdata_cancer; set final_dat; where cancer=1; run;
data rawdata_nocancer; set final_dat; where cancer=0; run;
```{r}
dat_cancer <- final_dat %>% filter(cancer == 1)
dat_nocancer <- final_dat %>% filter(cancer == 0)
```

# additional descriptive table for cancer group
```{r}
var_list <- c('age_cancer_gp', 'solid_tumor',
              'chemotherapy_1_month', 'chemotherapy_3_month', 'chemotherapy_6_month',
              'immunotherapy_1_month', 'immunotherapy_3_month', 'immunotherapy_6_month',
              'systemic_1_month', 'systemic_3_month', 'systemic_6_month',
              'radiation_1_month', 'radiation_3_month', 'radiation_6_month', 
              'survive_5yr_more')

(table_cancer_treatment <- descriptive_table(var_list, 'cancer', dat_cancer, showNA = 'ifany'))
```


<!-- %macro one_factor(rawdata_cancer,death); -->
<!-- proc datasets; delete S7-S19; run; -->

<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1, age_gp,7); -->
<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1,gender,8); -->
<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1,race_gp,9); -->
<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1,region,10); -->
<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1,N_comorbity_gp,11); -->
<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1,N_Posi_Comorb_gp,12); -->
<!-- %twoway_nominal2(&rawdata_cancer,&death, 0,1,surgery4wk,13); -->

<!-- data &rawdata_cancer.&death; -->
<!-- set S7-S13; -->
<!-- drop total; -->
<!-- id=_n_; -->
<!-- keep id variable level &death.1; -->
<!-- run; -->
<!-- proc sort data=&rawdata_cancer.&death; by id; run; -->
<!-- %mend; -->
```{r}
one_factor <- function(data, row_var_list, col_var, keep_one_row_name = TRUE, test=FALSE, ...) {
  
  table_lst <- list()
  for (i in 1:length(row_var_list)) {
     table_lst[[i]] <- two_way_table(data=data, row_var=row_var_list[i], col_var=col_var, keep_one_row_name=TRUE, test=test, margin = c('row'), ...)
  }
  
  com_indep <-  bind_rows(table_lst)
  com_indep <- com_indep %>% select(-c(sym(paste(col_var, 0)), 'Total'))
  
  return(com_indep)
}

```


# bug? colum sum not equal to 100%
```{r}
var_lst <- c('age_gp', 'gender', 'race_gp', 'region', 'n_comorbity_gp', 
             'n_posi_comorb_gp', 'surgery4wk')
dat_cancer_death <- one_factor(dat_cancer, var_lst, 'death')

dat_cancer_icu <- one_factor(dat_cancer, var_lst, 'icu')

dat_cancer_ventilation <- one_factor(dat_cancer, var_lst, 'ventilation')

dat_cancer_inpatient <- one_factor(dat_cancer, var_lst, 'inpatient')
```


data within_cancer;
merge rawdata_cancerdeath 
rawdata_cancerICU rawdata_cancerVentilation
rawdata_cancerinpatient;
by id;
run; 
```{r}
within_cancer <- cbind(dat_cancer_death,
'icu 1' = dat_cancer_icu[, 'icu 1'], 'ventilation 1'= dat_cancer_ventilation[, 'ventilation 1'],
'inpatient 1'= dat_cancer_inpatient[, 'inpatient 1'])
within_cancer 
```

%one_factor(rawdata_nocancer,death);
%one_factor(rawdata_nocancer,ICU);
%one_factor(rawdata_nocancer,Ventilation); 
%one_factor(rawdata_nocancer,inpatient); 
 
```{r}
dat_nocancer_death <- one_factor(dat_nocancer, var_lst, 'death')
dat_nocancer_icu <- one_factor(dat_nocancer, var_lst, 'icu')
dat_nocancer_ventilation <- one_factor(dat_nocancer, var_lst, 'ventilation')
dat_nocancer_inpatient <- one_factor(dat_nocancer, var_lst, 'inpatient')
```

data within_nocancer;
merge rawdata_nocancerdeath  
rawdata_nocancerICU rawdata_nocancerVentilation
rawdata_nocancerinpatient;
by id;
death1_noca= death1;
ICU1_noca=ICU1;
Ventilation1_noca=Ventilation1;
inpatient1_noca= inpatient1;
```{r}
within_nocancer <- cbind(dat_nocancer_death,
'icu1_noca' = dat_nocancer_icu[, 'icu 1'], 'ventilation1_noca'= dat_nocancer_ventilation[, 'ventilation 1'],
'inpatient1_noca'= dat_nocancer_inpatient[, 'inpatient 1'])
within_nocancer <- within_nocancer %>% rename('death1_noca' = 'death 1')
within_nocancer
```
# table 3

data Table3_part1;
merge within_cancer within_nocancer;
by id;
run;
```{r}
table3_part1 <- cbind(within_cancer, within_nocancer[, 3:ncol(within_nocancer)])
```

%macro one_factor_cancer(death);
proc datasets; delete S16-S20; run;
%twoway_nominal2(rawdata_cancer,&death, 0,1,cancer_type,16);
%twoway_digital2(rawdata_cancer,&death, 0,1,chemo_4w,17);
%twoway_digital2(rawdata_cancer,&death, 0,1,Radiation_4w,18);
%twoway_nominal2(rawdata_cancer,&death, 0,1,age_cancer_gp,19);
%twoway_digital2(rawdata_cancer,&death, 0,1,survive_5yr_more,20);

data cancer_&death;
set S16-S20;
drop total;
id=_n_;
keep id variable level &death.1;
run;
proc sort data=cancer_&death; by id; run;
%mend;


%one_factor_cancer(death);
%one_factor_cancer(ICU);
%one_factor_cancer(Ventilation); 
%one_factor_cancer(inpatient); 

data Table3_part2;
merge cancer_death  
cancer_ICU cancer_Ventilation
cancer_inpatient;
by id;  
run; 
```{r}
var_lst <- c('cancer_type', 'chemo_4w', 'radiation_4w', 'age_cancer_gp', 'survive_5yr_more')
dat_cancer_death <- one_factor(dat_cancer, var_lst, 'death')
dat_cancer_icu <- one_factor(dat_cancer, var_lst, 'icu')
dat_cancer_ventilation <- one_factor(dat_cancer, var_lst, 'ventilation')
dat_cancer_inpatient <- one_factor(dat_cancer, var_lst, 'inpatient')

table3_part2 <- cbind(dat_cancer_death,
'icu 1' = dat_cancer_icu[, 'icu 1'], 'ventilation 1'= dat_cancer_ventilation[, 'ventilation 1'],
'inpatient 1'= dat_cancer_inpatient[, 'inpatient 1'])
within_cancer 
```

data Table3;
set Table3_part1 Table3_part2;
run;
```{r}
table3 <- bind_rows(table3_part1, table3_part2)
# table3 <- table3 %>% select('variable', 'level', `death1_noca`:`inpatient1_noca`, everything())
table3
```


<!-- # Table 4, models; -->
<!-- data final_dat; -->
<!-- set B.final_dat; -->
<!-- if gender="Unknown" then gender=""; *to make missing not to participate in models; -->
<!-- if age_cancer_gp="miss" then age_cancer_gp="";   -->
<!-- if age_gp="z: Unk" then age_gp=""; -->
<!-- run; -->
<!-- ```{r} -->
<!-- # work_rawdata <- B_rawdata %>%  -->
<!-- #   mutate( -->
<!-- #     gender = factor(ifelse(gender == 'Unknown', NA, gender)), -->
<!-- #     age_cancer_gp = factor(ifelse(age_cancer_gp == 'miss', NA, age_cancer_gp)), -->
<!-- #     # age_gp = factor(ifelse(age_gp == 'z: Unknown', NA, age_gp)) -->
<!-- #     # n_comorbity = factor(n_comorbity), -->
<!-- #     # n_posi_comorb_gp = factor(n_posi_comorb_gp) -->
<!-- #   ) %>% droplevels() -->

<!-- # levels(work_rawdata$gender)[levels(work_rawdata$gender) == 'Unknown'] <-  NA -->
<!-- # levels(work_rawdata$age_cancer_gp)[levels(work_rawdata$age_cancer_gp) == 'miss'] <-  NA -->
<!-- # levels(work_rawdata$age_gp)[levels(work_rawdata$age_gp) == 'z: Unknown'] <-  NA -->
<!-- ``` -->

 
proc freq data=B.final_dat;
tables chemo_4w;
run;

```{r}
crosstable(final_dat, 'chemo_4w')
```

```{r}
crosstable(dat_cancer, t_30, age_gp, gender, race_gp, n_comorbity, n_posi_comorb,
  surgery_4w , cancer_type, chemo_4w, radiation_4w, survive_5yr_more)
```


# MODEL 1:Cox regression;

simple unadjusted model
```{r}
library(survival)
survival_model_simple <- coxph(Surv(t_30, death) ~ cancer, data = final_dat)

summary(survival_model_simple)
```
## check: the definition of those outcome variable (within what timeframe)
```{r}
model_simple_death_same_month <- glm(death_on_month_0 ~ cancer, data = final_dat, family = binomial(link = "logit"))
(model_simple_death_same_month_coef <- summary(model_simple_death_same_month))
ts_death <- model_simple_death_same_month_coef$coefficients[2, ]
```


```{r}
model_simple_inpatient <- glm(inpatient ~ cancer, data = final_dat, family = binomial(link = "logit"))
(model_simple_inpatient_coef <- summary(model_simple_inpatient))
ts_inpatient <- model_simple_inpatient_coef$coefficients[2, ]
```


```{r}
model_simple_ventilation <- glm(ventilation ~ cancer, data = final_dat, family = binomial(link = "logit"))
(model_simple_ventilation_coef <- summary(model_simple_ventilation))
ts_ventilation <- model_simple_ventilation_coef$coefficients[2, ]
```


```{r}
model_simple_icu <- glm(icu ~ cancer, data = final_dat, family = binomial(link = "logit"))
(model_simple_icu_coef <- summary(model_simple_icu))
ts_icu <- model_simple_icu_coef$coefficients[2, ]
```

```{r}
(ts <- rbind(ts_inpatient, ts_ventilation, ts_icu, ts_death))
```























<!-- # the following code is used to test equality of the data generated by R and SAS -->
<!-- ```{r} -->
<!-- dat <- read_sas('data/final_dat.sas7bdat') -->
<!-- ``` -->

<!-- ```{r} -->
<!-- colnames(dat) <- tolower(colnames(dat)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- dat <- dat %>% select(-c("p85", "p90", "p95", "p97")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- nrow(dat[, 1]) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- colname <- colnames(final_dat) -->
<!-- for(i in 1:ncol(dat)) { -->
<!--   print(colname[i]) -->
<!--   print(all(match(dat[, i], final_dat[, i]) == 1)) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- dat[dat == ''] <- NA -->
<!-- ``` -->


<!-- ```{r} -->
<!-- # dat <- dat %>% mutate(smoke = ifelse(is.na(smoke), NA, smoke)) -->
<!-- all(dat[!is.na(dat$smoke_by_icd_group), ]$smoke_by_icd_group == final_dat[!is.na(final_dat$smoke_by_icd_group), ]$smoke_by_icd_group) -->
<!-- ``` -->
<!-- ``` -->


<!-- ```{r} -->
<!-- colnames(final_dat) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- colnames(dat) -->
<!-- ``` -->

