---
title: "step3 calculate the rests"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
library(summarytools)
```


```{r}
load('data/rawdata2.Rdata')
```

```{r}
proc_freq <- function(data, vars) {
  for (var in vars) {
    print(var)
    print(freq(x = data[[var]]))
  }
}
```


```{r}
proc_freq(rawdata2, c('chronic_kidney_disease', 'chronic_obstructive_pulmonary', 'down_syndrome', 'solid_organ_transplant',                              'obesity01', 'pregnancy', 'heart_failure', 'coronary_artery_disease', 'cardiomyopathies', 'sickle_cell_disease', 'smoke_yn', 'type_2_diabetes_mellitus'))
```

## bug??
```{r}
# data rawdata3; set rawdata2;
# N_comorbity=sum(Chronic_Kidney_Disease,
# Chronic_Obstructive_Pulmonary,Down_Syndrome,     # bug? sum will ignore missing value
# Solid_Organ_Transplant,
# obesity01,pregnancy,
# Heart_Failure,Coronary_Artery_Disease, 
# Cardiomyopathies,
# Sickle_Cell_Disease,smoke_yn,Type_2_Diabetes_Mellitus);
# 
# N_Posi_Comorb=sum(Asthma,Cerebrovascular,Cystic_Fibrosis,
# Hypertension,Other_Immuno,Liver_Disease,Dementia,
# overweight01,Pulmonary_Fibrosis,Thalassemia,Type_1_Diabetes_Mellitus);

rawdata3 <- rawdata2 %>% 
  rowwise() %>% 
  mutate(n_comorbity = sum(chronic_kidney_disease, chronic_obstructive_pulmonary, down_syndrome, solid_organ_transplant,                              obesity01, pregnancy, heart_failure, coronary_artery_disease, cardiomyopathies, sickle_cell_disease, smoke_yn, type_2_diabetes_mellitus, na.rm = TRUE),

        n_posi_comorb=sum(asthma,cerebrovascular,cystic_fibrosis,
hypertension,other_immuno,liver_disease,dementia,
overweight01,pulmonary_fibrosis,thalassemia,type_1_diabetes_mellitus, na.rm = TRUE))
```


```{r}
# if N_comorbity>=4 then N_comorbity_gp=">=4";
# else if N_comorbity=3 then N_comorbity_gp="3";
# else if N_comorbity=2 then N_comorbity_gp="2"; 
# else if N_comorbity=1 then N_comorbity_gp="1";
# else if N_comorbity~=. then N_comorbity_gp="0";
# 
# if N_Posi_Comorb>=4 then N_Posi_Comorb_gp=">=4";
# else if N_Posi_Comorb=3 then N_Posi_Comorb_gp="3";
# else if N_Posi_Comorb=2 then N_Posi_Comorb_gp="2";
# else if N_Posi_Comorb=1 then N_Posi_Comorb_gp="1"; # bug 0 is not considered
# else if N_Posi_Comorb~=. then N_Posi_Comorb_gp="0";


# create categorized n_comorbity variable and n_posi_comorb
rawdata3 <- rawdata3 %>% 
  # rowwise() %>% 
  mutate(n_comorbity_gp = ifelse(is.na(n_comorbity), NA,  # treat missing as 0 ? could be bug?
                                       ifelse(n_comorbity >= 4, '>=4',
                                              ifelse(n_comorbity == 3, '3',
                                                     ifelse(n_comorbity == 2, '2',
                                                            ifelse(n_comorbity == 1, '1', '0')
                                                            )
                                                     )
                                              )
                                 ),
         n_posi_comorb_gp = ifelse(is.na(n_posi_comorb), NA, # treat missing as 0 ? could be bug?
                                       ifelse(n_posi_comorb >= 4, '>=4',
                                              ifelse(n_posi_comorb == 3, '3',
                                                     ifelse(n_posi_comorb == 2, '2',
                                                            ifelse(n_posi_comorb == 1, '1', '0')
                                                            )
                                                     )
                                              )
                                 )
         )
```

#bug!!!!!!!!!!!!!
```{r}
# if MA_Cytotoxic_4w=1 or PS_Cytotoxic_4w=1 or PR_Cytotoxic_4w=1 then cytotoxic_4wk="Y";
# else cytotoxic_4wk="N";
# 
# if MA_Non_Cytotoxic_4w=1 or PS_Non_Cytotoxic_4w=1 or PR_Non_Cytotoxic_4w=1 then Nocytotoxic_4wk="Y";
# else Nocytotoxic_4wk="N";
#


# if cytotoxic_4wk="Y" then cytotoxic4wk="a. cytotoxic  ";                         # extra whitespace


# else if Nocytotoxic_4wk="Y" then cytotoxic4wk="b. no cytotoxic";                 
# else cytotoxic4wk="c. no chemo drug";
# 
# *combine cytotoxic drug;
# if cytotoxic4wk in ("a. cytotoxic","b. no cytotoxi") then chemo_4w=1;            # variable value not match
# else if cytotoxic4wk="c. no chemo dr" then chemo_4w=0;                           # variablke value not match (c. no chemo dr)
# 
# run;


rawdata3 <- rawdata3 %>% 
  rowwise() %>% 
  # if NA is encountered in condition statement, NA will be return directly
  mutate(cytotoxic_4wk = ifelse(ma_cytotoxic_4w == 1 || ps_cytotoxic_4w == 1 || pr_cytotoxic_4w == 1, 'Y', 'N'),
         nocytotoxic_4wk = ifelse(ma_non_cytotoxic_4w == 1 || ps_non_cytotoxic_4w == 1 || pr_non_cytotoxic_4w == 1, 'Y', 'N'),
         cytotoxic4wk = ifelse(cytotoxic_4wk == 'Y', 'a. cytotoxic', 
                               ifelse(nocytotoxic_4wk == 'Y', 'b. no cytotoxic', 'c. no chemo drug')),
         # combine cytotoxic drug
         chemo_4w = ifelse(cytotoxic_4wk == 'Y' || nocytotoxic_4wk == 'Y', 1, 
                           ifelse(cytotoxic_4wk == 'N' && cytotoxic_4wk == 'N', 0, NA))
         
         )

```



proc freq data=rawdata3;
tables N_comorbity_gp  N_Posi_Comorb_gp cytotoxic_4wk
Nocytotoxic_4wk cytotoxic4wk chemo_4w;
where cancer=1;
run;
/*
proc freq data=rawdata2;
tables       Chronic_Kidney_Disease 
Chronic_Obstructive_Pulmonary Down_Syndrome 
Solid_Organ_Transplant 
obesity01 pregnancy 
Heart_Failure Coronary_Artery_Disease  
Cardiomyopathies 
Sickle_Cell_Disease smoke_yn Type_2_Diabetes_Mellitus
Asthma Cerebrovascular Cystic_Fibrosis 
Hypertension Other_Immuno Liver_Disease Dementia 
overweight01 Pulmonary_Fibrosis Thalassemia Type_1_Diabetes_Mellitus
;
run;*/
```{r}
# vars <- c('n_comorbity_gp', 'n_posi_comorb_gp', 'cytotoxic_4wk', 'nocytotoxic_4wk', 'cytotoxic4wk', 'chemo_4w')
# for (var in vars) {
#   print(var)
#   print(freq(x = rawdata3[rawdata3$cancer == 0, ][[var]]))
# }
```

```{r}
# data rawdata4;
# set rawdata3; 
# cancer_year=year(cancer_date);
# 
# age_at_cancer=(cancer_year-BIRTH_YR);
# 
# duration=(COVID_diag_date-cancer_date)/365.25;
# if duration>5 then survive_5yr_more=1;
# else if duration<=5 and duration>=0 then survive_5yr_more=0;
# if cancer=0 then survive_5yr_more=.;
# 
# *IF the cancer occur before covid, then need to be labeled and deleted later;
# if duration<0 and duration~=. then cancer_after_COVID=1;
# 
# if age_at_cancer>=0 and age_at_cancer<20 then age_cancer_gp="0-20  ";
# else if age_at_cancer>=20 and age_at_cancer<40 then age_cancer_gp="20-40";
# else if age_at_cancer>=40 and age_at_cancer<60 then age_cancer_gp="40-60";
# else if age_at_cancer>=60 and age_at_cancer<80 then age_cancer_gp="60-80";
# else if age_at_cancer>=80 then age_cancer_gp=">=80";
# else age_cancer_gp="miss";


rawdata4 <- rawdata3 %>% 
  # rowwise() %>% 
  mutate(cancer_year = as.numeric(format(`cancer_date`, "%Y"))
         )


```

```{r}


rawdata4 <- rawdata4 %>% 
  rowwise() %>% 
  mutate(
         age_at_cancer = (cancer_year - birth_yr),
         duration = as.numeric(`covid diag date` - cancer_date)/365.25,

         survive_5yr_more = ifelse(duration > 5, 1,
                                   ifelse(duration >=0 && duration <=5, 0, NA)),
         # override survive_5yr_more with special condition
         survive_5yr_more = ifelse(cancer == 0, NA, survive_5yr_more),

         # if the cancer occur before covid, then need to be labeled and deleted later;
         cancer_after_covid = ifelse(duration < 0, 1, NA),


         )

```



```{r}
rawdata4 <- rawdata4 %>% 
  # rowwise() %>% 
  mutate(age_cancer_gp = ifelse(age_at_cancer >= 0 && age_at_cancer < 20, '0-20', 
                                ifelse(age_at_cancer >= 20 && age_at_cancer < 40, '20-40', 
                                       ifelse(age_at_cancer >= 40 && age_at_cancer < 60, '40-60',
                                              ifelse(age_at_cancer >= 60 && age_at_cancer < 80, '60-80',
                                                     ifelse(age_at_cancer >= 80, '>=80', "miss"))))))
```


```{r}
# proc freq data=rawdata4;
# tables age_cancer_gp Radiation_4w;
# where cancer=1;
# run;

vars <- c('age_cancer_gp','radiation_4w')
proc_freq(rawdata4[rawdata4$cancer == 1, ], vars)

```



##bug!!!!!!!!!!
```{r}
# data rawdata5;
# set rawdata4;
# time_death=DATE_OF_DEATH-COVID_diag_date;
# if time_death>=-15 and time_death<0 then time_death=0;*If it is within 15 days then set it as 0 (because we do not know death date but assuming mid of the month), immediately die after covid;
# if time_death~=. and time_death<-15 then time_death=.; *if the value is way below 15, treat it as missing;
# end_study=mdy("01","28","2021");
# format end_study mmddyy10.;
#  
# if death=1 then T=time_death;
# else if death=0 then T=(end_study-COVID_diag_date);
# 
# *if T<0 then T=.; *for those whose COVID_diag_date is over 
# *For those die after 30 days, death will be changed to "0" (means no death);
# T_greater_30=0;
# if death=1 and time_death>30 then do; T_greater_30=1; death=0;end;                # missing death will always < 30
# 
# if T~=. then T_30=min(T,30);
# 
# run;

rawdata5 <- rawdata4 %>% 
  # rowwise() %>% 
  mutate(time_death = as.numeric(date_of_death - `covid diag date`),
         time_death = ifelse(time_death >= -15 && time_death < 0, 0, 
                             ifelse(time_death < -15, NA, time_death)),
         end_study = as.Date('2021-01-28')
         )


```

```{r}
rawdata5 <- rawdata5 %>% 
  rowwise() %>% 
  mutate(t = ifelse(death == 1, time_death, 
                    ifelse(death == 0, as.numeric(end_study - `covid diag date`))),
         t = ifelse(t < 0, NA, t),
         t_greater_30 = ifelse(is.na(time_death), NA, 
                               ifelse(death == 1 && time_death > 30, 1, 0)),
         death = ifelse(is.na(time_death), death, 
                        ifelse(death == 1 && time_death > 30, 0, death)), 
         t_30 = min(t, 30))
```


```{r}
# proc_means <- function(data, vars) {
#   for(var in vars) {
#     print()
#   }
# }

min(rawdata5[rawdata5$death == 1, ]$t_30, na.rm = TRUE)
```


```{r}
# proc print data=rawdata5 (obs=20);
# var death DATE_OF_DEATH COVID_diag_date  time_death T T_30;
#  run;

head(rawdata5[, c('death', 'date_of_death', 'covid diag date', 'time_death', 't', 't_30')], 20)
```



```{r}
# proc freq data=rawdata4;
# tables death;
# run;

proc_freq(rawdata4, c('death'))
```


```{r}
# proc freq data=rawdata5;
# tables death;
# run;

proc_freq(rawdata5, c('death'))
```

##typo !!!!!
```{r}
# data rawdata6;
# set rawdata5;
# cancer_2digit=substr(Cancer_dx_code,1,3);
# 
# if cancer_2digit
# in ("C10", "C11", "C12", "C13", "C14", "C15", "C16", "C17", "C18", "C19", "C20",
#     "C21", "C22", "C23", "C24", "C25", "C26", "C30", "C31", "C32", "C33", "C34",
#     "C37", "C38", "C39", "C40", "C41", "C43", "C45", "C46", "C47", "C48", "C49",
#     "C50", "C51", "C52", "C53", "C54", "C55", "C56", "C57", "C58", "C60", "C61",
#     "C62", "C63", "C64", "C65", "C66", "C67", "C68", "C69", "C70", "C71", "C72",
#     "C73", "C74", "C75" ) then cancer_type="a. solid    ";                         # unnecessary trailing whitespace
# else if cancer_2digit in ("C81", "C82", "C83", "C84","C85", "C88", "C90", "C91",
#   "C92", "C93", "C94", "C95", "C96") then cancer_type="b. liquid";
# else if cancer_2digit="C76" then cancer_type="c.Multitype";
# if Region="Other/Unknown" then Region="z: Other/Unknown";
# run;
#  

solid_cancer_codes <- c("C10", "C11", "C12", "C13", "C14", "C15", "C16", "C17", "C18", "C19", "C20",
    "C21", "C22", "C23", "C24", "C25", "C26", "C30", "C31", "C32", "C33", "C34",
    "C37", "C38", "C39", "C40", "C41", "C43", "C45", "C46", "C47", "C48", "C49",
    "C50", "C51", "C52", "C53", "C54", "C55", "C56", "C57", "C58", "C60", "C61",
    "C62", "C63", "C64", "C65", "C66", "C67", "C68", "C69", "C70", "C71", "C72",
    "C73", "C74", "C75" )

liquid_cancer_codes <- c("C81", "C82", "C83", "C84","C85", "C88", "C90", "C91",
   "C92", "C93", "C94", "C95", "C96")

rawdata6 <- rawdata5 %>% 
  rowwise() %>% 
  mutate(cancer_2digit = substr(cancer_dx_code, 1, 3),
         cancer_type = ifelse(cancer_2digit %in% solid_cancer_codes, 'a. solid', 
                              ifelse(cancer_2digit %in% liquid_cancer_codes, 'b. liquid',
                                     ifelse(cancer_2digit == 'C76', 'c.Multitype', NA))),
         region = ifelse(region == 'Other/Unknown', 'z: Other/Unknown', region)
         
         )

```

```{r}
# proc freq data=rawdata6;
# tables Cancer_dx_code cancer_2digit  ;
# where cancer=1;
# run;

# proc_freq(rawdata6[rawdata6$cancer == 1, ], c('cancer_dx_code', 'cancer_2digit'))
```


```{r}
# proc freq data=rawdata6;
# tables death inpatient ICU Ventilation;
# run;


proc_freq(rawdata6, c('death', 'inpatient', 'icu', 'ventilation'))
```
# bug!!!
```{r}
# data rawdata7;
# set rawdata6;
# if death=0 and inpatient=0 and ICU=0 and Ventilation=0 then severity_level=0;
# else if death=0 and inpatient=1 and ICU=0 and Ventilation=0 then severity_level=1;
# else if death=1 then severity_level=3;
# else if death~=. and inpatient~=. and ICU~=. and
# Ventilation~=. then severity_level=2;
# 
# if death=. then delete; *in outcomes, only death has missing;
# if cancer_after_COVID=1 then delete;   # cancer_after_COVID only have missing and 1 two values
# run;

rawdata7 <- rawdata6 %>% 
  rowwise() %>% 
  mutate(severity_level = ifelse(death == 0 && inpatient == 0 && icu == 0 && ventilation == 0, 0,
                                 ifelse(death == 0 && inpatient == 1 && icu == 0 && ventilation == 0, 1, 
                                        ifelse(death == 1, 3, 2)))
         ) %>% 
  filter(!is.na(death)) %>% 
  filter(is.na(cancer_after_covid) || !(cancer_after_covid == 1)) # code logic weired
```


```{r}
# convert some variable to factor with level order
rawdata7 <- rawdata7 %>% 
  mutate(severity_level = factor(severity_level, levels=c('0', '1', '2', '3')),
         age_gp = factor(age_gp, levels=c('0-18', '18-50', '50-65', '65-75', '>= 75')),
         n_comorbity_gp = factor(n_comorbity_gp, levels = c('0', '1', '2', '3', '>=4')),
         n_posi_comorb_gp = factor(n_posi_comorb_gp, levels = c('0', '1', '2', '3', '>=4'))
         )
```


```{r}
# proc freq data=rawdata7;
# tables severity_level severity smoke_status;
# run;

proc_freq(rawdata7, c('death', 'severity_level', 'severity', 'smoke_status'))
```


```{r}
# data B.rawdata;
# set rawdata7;
# where age>=18;
# run;

B_rawdata <- rawdata7 %>% 
  filter(age >= 18)

save(B_rawdata, file = 'data/B_rawdata.RData')
```

```{r}
proc_freq(rawdata, c('death', 'severity_level', 'severity', 'smoke_status'))

```
```{r}
# *check how many missings in obesity;
# proc freq data=rawdata7;
# tables obesity01 overweight01 N_comorbity_gp N_Posi_Comorb_gp;
# *where BMI>0 and BMI<18.5 and age_in_month=240;
# where cancer=0 and age>=18;
# run;


proc_freq(rawdata7, c('smoke_yn', 'obese_overweight', 'obesity01', 'overweight01', 'n_comorbity_gp', 'n_posi_comorb_gp'))
```

